Fréchet Distance

### 2022-12-05 docs/paper.tex
free space monotone curve
add Fréchet distance example figure

@@

\begin{figure}[ht]
  \centering
  % TODO: Add example graphic of Frechet distance
  \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
  \caption{The Fréchet distance is indicated by the black lines connecting the two polygonal curves.}
  \label{fig_frechet_distance_example}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  % TODO: Replace graphic with appropiate example
  \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
  \caption{The monotonically increasing curve (red) through the free space diagram.}
  \label{fig_free_space_curve}
\end{figure}

>>>>

\usepackage{svg}

@@

\begin{figure}[ht]
  \centering
  % TODO: Add example graphic of Frechet distance
  % \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
  \includesvg{images/frechet_distance/frechet-distance-example.svg}
  \caption{The Fréchet distance is indicated by the black lines connecting the two polygonal curves.}
  \label{fig_frechet_distance_example}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \resizebox{0.5\textwidth}{!}{
    \input{images/frechet_distance/free_space_monotone_curve.tex}
  }
  \caption{A monotonically increasing curve (red) through the free space diagram.}
  \label{fig_free_space_curve}
\end{figure}
